\chapter*{Dedication}
\thispagestyle{empty}
\begin{singlespace}

\vspace{1cm}

\noindent This work is the reflection of the boundless love and unwavering
support that have illuminated every step of my life and of my academic
journey.

\bigskip

\noindent To my beloved father, \textbf{Mondher}, you have been the quiet
strength behind every milestone I have reached. From the earliest days of
my schooling to the choice of the most demanding schools and universities,
you stood by me with patience, sacrifice and a steady hand. The values of
discipline, perseverance and integrity that guide me today are nothing more
than the daily example you have set. No words could ever match the
gratitude I owe you.

\bigskip

\noindent To my dearest mother, \textbf{Hajer}, you are the warmth and the
soul of our home. Your tender care, your endless patience and the countless
nights you spent watching over my studies have shaped the person I have
become. Even now, you continue to surround me with attention so that
nothing is ever missing from my path. Your love is the most precious gift
of my life, and for that I will be forever thankful.

\bigskip

\noindent To my elder sister, \textbf{Minyar}, your kindness, complicity
and constant encouragement have been a true blessing. As you prepare for
the \textit{baccalauréat}, I wish you the courage, the calm and the success
you deserve, and may this milestone open the doors of the future you dream
of.

\bigskip

\noindent To my little sister, \textbf{Maram}, your laughter and your
spontaneous affection bring light to every ordinary day. As you face your
ninth-grade national exam, I wish you confidence, focus and a brilliant
result, and I have no doubt that you are about to make us all proud.

\bigskip

\noindent To my dear friends, my faithful companions through the highs and
lows of these years, your loyalty, your humour and the moments we have
shared have made this journey infinitely richer. Your support has been
quietly woven into every success I have reached, and I am truly grateful
for each of you.

\bigskip

\noindent To all of you, with love and gratitude, I dedicate this humble work.

\vspace{\fill}

\begin{flushright}
\textbf{Oussema Aissaoui}
\end{flushright}
\end{singlespace}
