\chapter*{Acknowledgements}
\thispagestyle{empty}
\begin{singlespace}

\vspace{1cm}

\noindent The completion of this graduation project owes much to the
people who guided, supported and trusted me throughout the internship,
and I am glad to take this opportunity to express my sincere gratitude.

\bigskip

\noindent I would first like to thank my academic supervisor,
\textbf{Mrs. Dorra Dhouib}, from the \textit{École Nationale des Sciences
de l'Informatique (ENSI)}, for her attentive guidance, her constructive
feedback and the academic rigour with which she shaped the direction of
this work.

\bigskip

\noindent I would also like to express my sincere appreciation to
\textbf{Mrs. Imen Ayari}, head of the Innovation Factory department, for
the welcoming environment, the institutional support and the trust placed
in me throughout this internship.

\bigskip

\noindent My deepest thanks go to my company supervisors at
\textit{Talan Tunisie Consulting}, \textbf{Mrs. Yosr Omrane} and
\textbf{Mrs. Hayfa Grayet}, whose technical expertise, availability and
trust were decisive at every milestone of the project. Their thoughtful
insights consistently elevated the quality of the proposed solution.

\bigskip

\noindent My gratitude further extends to the entire team of the
\textit{Innovation Factory} at Talan Tunisie Consulting, whose
collaborative spirit, technical generosity and daily encouragement created
an inspiring setting in which to learn, build and grow.

\bigskip

\noindent Finally, I wish to thank the members of the jury for the honour
of evaluating this work and for the time devoted to its review.
\end{singlespace}
